---
title: "Homework_07"
author: "Paulina Murray"
date: "3/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
library(tidyverse) # for tidying my data
library(dplyr)
library(tidyr)
library(stringr)
```

```{r}
# reading enzyme data into R
z <- read.table("SCG_Enzymes.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)

# cleaning my data

## add columns treatment and sample type
treatment <- c("Quarter Gap", "Quarter Gap", "Thinning Matrix", "Thinning Matrix", "Acre Gap", "Acre Gap", "Acre Gap", "Thinning Matrix", "Quarter Gap", "Control", "Control", "Control")
sample_type <- c("soil","soil","soil","soil","soil","soil","soil","soil","soil","soil","soil","soil","wood","wood","wood","wood","wood","wood","wood","wood","wood","wood","wood","wood")
z$treatment <- treatment
z$sample_type <- sample_type

z$treatment <- factor(z$treatment, levels = c("Control", "Thinning Matrix", "Quarter Gap", "Acre Gap"))

## gather = makes "wide" data "long"
## gather(data, key, measurement, arguments to include)
z <- tidyr::gather(z, enzyme, activity, BG:LAP)

## consolidating data
z$sample_ID <- str_remove_all(z$sample_ID, "[SW]") # dropping "S/W" distinction
z$sample_ID <- as.factor(z$sample_ID) # converting data
z$enzyme <- as.factor(z$enzyme)
z$enzyme <- droplevels(z$enzyme)

# subsetting soil samples from original data
#z <- subset(z,sample_type == "soil")

# subsetting activities from one enzyme
#z <- subset(z,enzyme == "BG")

```

```{r}
# quick and dirty, a truncated normal distribution to work on the solution set

# z <- rnorm(n=3000,mean=0.2)
# z <- data.frame(1:3000,z)
# names(z) <- list("ID","myVar")
# z <- z[z$myVar>0,]
# str(z)
# summary(z$myVar)
```

```{r}
# histogram of enzymatic activities in soil 7 enzymes
p1 <- ggplot(data=z, aes(x=activity)) +
  geom_histogram(aes(stat="identity"),color="grey60",fill="cornsilk",size=0.2)
print(p1)
```

```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```

```{r}
normPars <- fitdistr(z$activity,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute
```

```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$activity),len=length(z$activity))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$activity), args = list(mean = meanML, sd = sdML))
 p1 + stat
```

```{r}
expoPars <- fitdistr(z$activity,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$activity), args = list(rate=rateML))
 p1 + stat + stat2
```

```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$activity), args = list(min=min(z$activity), max=max(z$activity)))
 p1 + stat + stat2 + stat3
```

```{r}

z$activity <- ifelse(z$activity == 0, 1, z$activity) # remove zeros for gamma

gammaPars <- fitdistr(z$activity,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$activity), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

```{r}
pSpecial <- ggplot(data=z, aes(x=activity/(max(activity + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$activity/max(z$activity + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = activity, y = sample_ID), fun = dbeta, colour="orchid", n = length(z$activity), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

I am using my data that i collected at the Second College Grant in New Hampshire. I collected wood and soil samples within different silvicultural forest management treatments and analyzed them for the activities of 7 different enzymes that are known to be related to carbon, nitrogen, and phosphorous cycling in forest ecosystems. 

My data are not normal and heavily skewed towards zero which is very different from the normally distributed data we generated. I think the beta distribution best fit my data.
